\bf Landslide: Systematic Testing in 15-410 \\ Sign-Up Sheet

### 2015-02-10 irb/hurdle.tex
update hurdle sign up

	\\
	\checkbox{We have {\em attempted}, but do not necessarily pass, the following stress tests; and {\em attempted} to debug and fix any observed bugs: {\tt juggle 4 3 2 0}; {\tt multitest}; {\tt racer} (for 15 minutes); {\tt paraguay}.}

>>>>

	\\
	\checkbox{We have {\em attempted}, but do not necessarily pass, the following stress tests: {\tt juggle 4 3 2 0}; {\tt multitest}; {\tt racer} (for 15 minutes); {\tt paraguay}.}
